\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-07 k-planar.tex
updates
Partial commit

  The proof is by induction on the number of inner faces of $N$.  If $N$ has one inner face, then we can simply take $\mathcal{P}:=\{P_1,\ldots,P_k\}$ and verify the preconditions of the lemma (the setup) ensure that $\mathcal{P}$ satisfies the requirements of the lemma.  Therefore, we may assume that $N$ has at least two inner faces.

>>>>

  The proof is by induction on the number of inner vertices of $N$, i.e., on $|V(N)\setminus V(F)|$.  If $N$ has no inner vertices, then we can simply take $\mathcal{P}:=\{P_1,\ldots,P_k\}$ and verify the preconditions of the lemma (the setup) ensure that $\mathcal{P}$ satisfies the requirements of the lemma.  Therefore, we may assume that $N$ has at least one inner vertex.
